PubCrawl: A Publication Search Engine

### 2012-05-18 report/paper.tex
Define N in the equation

where $R(\cdot)$ is the PageRank of a node, $D(\cdot)$ is the outdegree of a
node, $E(\cdot)$ is the score source of a node (needed to converge with
cycles), $C(\cdot)$ is the component containing a node, $d$ is the damping
factor, and $n$ is the normalizing factor.

@@

>>>>

where $R(\cdot)$ is the PageRank of a node, $D(\cdot)$ is the outdegree of a
node, $E(\cdot)$ is the score source of a node (needed to converge with
cycles), $C(\cdot)$ is the component containing a node, $N$ is the total number
of papers, $d$ is the damping factor, and $n$ is a normalizing factor.

@@

We acknowledge Adam Marcus and Eugene Wu for their assistance with the user
studies.
